Music Recommendation System Using the Million Song Dataset

### 2015-05-07 writeup/MSDgroupwriteup.tex
Update MSDgroupwriteup.tex

\begin{document}
\title{Clustering of Last.fm Music}

@@

\subsection{Data}
The main source of data for this project was the Million Song Data Set (MSD)  \citep{Bertin-Mahieux2011}. We used the sample data set from the Kaggle competition which contains tuples of user id, song id, and play count.

@@

We choose to subset the data to users who have listened to more than 27 songs and songs which were listened to by more than 22 users. This resulted in a dataset which was 10\% the size of the original. Despite subsetting the data, we are still dealing with a matrix of $8130$ users by $11861$ songs, so some of our algorithms will take a fair amount of time to run.

\subsubsection{Data Statistics}

@@

$$w_i = \sum_{v \epsilon V} sim(u, v)$$

@@

$$w_b = \sum_{a \epsilon A} sim(a, b)$$

>>>>

\begin{document}
\title{Music Recommendation System Using the Million Song Dataset}

@@

\subsection{Data and Statistics}
The main source of data for this project was the Million Song Data Set (MSD)  \citep{Bertin-Mahieux2011}. We used the sample data set from the Kaggle competition which contains tuples of user id, song id, and play count.

@@

We choose to subset the data to users who have listened to more than 27 songs and songs which were listened to by more than 22 users. This resulted in a dataset which was 10\% the size of the original. The sparsity of the data was .0016, meaning that we only had play counts for 0.16\% of the user, song pairs (i.e. not all users listen to all songs). Despite subsetting the data, though, we are still dealing with a matrix of $8130$ users by $11861$ songs, so some of our algorithms will take a fair amount of time to run.

@@

$$w_i = \sum_{v \in V} sim(u, v)$$

@@

$$w_b = \sum_{a \in A} sim(a, b)$$
